Matching bullets

### 2015-11-17 imaging-paper.Rnw
figure width
added code and different view

\begin{figure}
\includegraphics[width=\textwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}
\section{Application}

>>>>

\begin{figure}
<<side-by-side, echo=FALSE, eval=FALSE>>=
paths <- file.path(datadir, dir(datadir))

br111 <- read.x3p(paths[5])
crosscuts <- unique(fortify_x3p(br111)$x)
crosscuts <- crosscuts[crosscuts > 50]
crosscuts <- crosscuts[crosscuts < 150]

list_of_fits <- lapply(crosscuts, function(x) {
  br111 <- get_bullet(paths[5], x = x)
  br111.groove <- get_grooves(br111)
  br111.groove$plot
  fit_loess(br111, br111.groove)
})

lof <- lapply(list_of_fits, function(x) x$resid$data) %>% bind_rows

br111 <- read.x3p(paths[7])
crosscuts <- unique(fortify_x3p(br111)$x)
crosscuts <- crosscuts[crosscuts > 50]
crosscuts <- crosscuts[crosscuts < 150]

list_of_fits2 <- lapply(crosscuts, function(x) {
  br111 <- get_bullet(paths[7], x)
  br111.groove <- get_grooves(br111)
  br111.groove$plot
  fit_loess(br111, br111.groove)
})

lof2 <- lapply(list_of_fits2, function(x) x$resid$data) %>% bind_rows
lof$bullet <- 1
lof2$bullet <- 2

LOF <- rbind(lof, lof2)

subLOF1 <- LOF %>% filter(bullet == 1, x <= 100)
subLOF2 <- LOF %>% filter(bullet == 2, x > 100)

subLOF <- rbind(data.frame(subLOF1), data.frame(subLOF2))
subLOF1$y <- subLOF1$y + 19*1.5625 # working now!!!
subLOF <- rbind(data.frame(subLOF1), data.frame(subLOF2))

qplot(x, y, fill = resid, colour=I(NA), data=subLOF, geom="tile") + 
  scale_fill_gradientn(limits=c(-5,5), 
                       colors=c("grey5", "gold4","darkgoldenrod1","lightgoldenrod1", "lemonchiffon"),
                       values = c(0,0.5, 0.75, 0.9, 1)) +
  theme_bw()
@

\includegraphics[width=\columnwidth]{images/side-by-side-manual-match.png}
\caption{\label{fig:manualmatch}\hh{Manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}

\begin{figure}
\includegraphics[width=\columnwidth]{images/match-rgl.png}
\caption{\label{fig:manualmatch}\hh{Different view of the manually adjusted side-by-side comparison of two lands from different bullets.}}
\end{figure}

\section{Application}
